Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] finish MC appendix

Now we present the yet allowed ranges due to non-standard tensor and
scalar couplings of the so far unmeasured angular observables
$J_{6c}$, $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to
K^*(\to K\pi)\bar\ell\ell$ in order to explore the potential of their
future measurements in fits of the kind pursued in this work.  The
68\% probability intervals are collected in \reftab{tab:postdictions}
for the various model-independent scenarios, allowing for interference
with non-zero vector couplings, in \refsec{sec:tensor},
\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for
$q^2$-integrated quantities in the low- and high-$q^2$ bins $q^2\in
[1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$ GeV$^2$,
respectively. Their posterior distributions have been obtained from
the final posterior samples as explained in~\cite{Beaujean:2012uj}
\todo{check uncertainty propagation there}.

@@

\section{Monte Carlo sampling}
\label{app:mc}
\todo{reference in main text}
The marginalization of the posterior is performed with the package {\tt
  pypmc}~\cite{beaujean_2015_20045}, which incorporates the algorithm presented
in \cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an implementation
of the variational Bayes algorithm. In every analysis we first run multiple
adaptive Markov chains (MCMC) in parallel through \texttt{pypmc}. If necessary,
chains are seeded at the SM point to exclude solutions in which multiple
nuisance parameters simultaneously deviate strongly from prior expectations.

@@

In all but three cases, the Markov chains then give reliable results. But when
we analyze scenarios with $\wilson[NP]{S,P} \ne 0$ and all exp.  constraints,
strong correlations appear again. As a final solution, we then use importance
sampling with the initial proposal function determined by a fit of a Gaussian
mixture to the MCMC samples within the variational Bayes approximation. As the
posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
components are need; i.e., 3 components proved optimal by the variational
approximation to the model evidence. In the most challenging run with 62
parameters, we obtain a relative effective sample size of only 0.038\%. We want
to have enough samples such that the 68\% region is determined with a relative
precision of about 1\%. As a rule of thumb, we consider the ``relative error of
the error'' given by $1/\sqrt{2 N_{\rm eff}}$~\cite[ch. 37]{Agashe:2014kda}.

% consider the binomial model with flat
% prior. Then the standard deviation over the mean of the posterior on the
% binomial parameter $p$ is $\sqrt{ \frac{1-p}{N_{\rm eff} p}}$ where $N_{\rm
%   eff}$ is the number of independent samples.

In the 62D case, we compute $1.1\cdot10^6$ importance samples such that $N_{\rm
  eff} \approx 3500$ and the estimated relative error of the error is 1.2\% and
thus good enough for our purposes.

To create the smooth marginal plots in Figures
\ref{fig:FHvsCT}--\ref{fig:scalar:SM-EFT}, we apply kernel density estimation
for MCMC and importance samples using the fast \texttt{figtree}
library~\cite{morariu08figtree}. In the latter case, we additionally crop 500
outliers.

>>>>

Now we present the yet allowed ranges due to non-standard tensor and scalar
couplings of the so far unmeasured angular observables $J_{6c}$, $(J_{1s} - 3\,
J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$ in order to
explore the potential of their future measurements in fits of the kind pursued
in this work.  The 68\% probability intervals are collected in
\reftab{tab:postdictions} for the various model-independent scenarios, allowing
for interference with non-zero vector couplings, in \refsec{sec:tensor},
\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for $q^2$-integrated
quantities in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and
$q^2\in [15,\, 19]$ GeV$^2$, respectively. Their posterior distributions have
been obtained from the posterior samples as explained in~\ref{app:mc}.

@@

\section{Monte Carlo sampling}
\label{app:mc}
\todo{reference in main text} The marginalization of the posterior is performed
with the package {\tt pypmc}~\cite{beaujean_2015_20045}, which incorporates the
algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition
an implementation of the variational Bayes algorithm. In every analysis we first
run multiple adaptive Markov chains (MCMC) in parallel through
\texttt{pypmc}. If necessary, chains are seeded at the SM point to exclude
solutions in which multiple nuisance parameters---mostly for hadronic
corrections---simultaneously deviate strongly from prior expectations.

@@

In all but three cases, the Markov chains then give reliable results. But when
we analyze scenarios with $\wilson[NP]{S,P} \ne 0$ and all exp.  constraints,
strong correlations appear again. As a final solution, we then use importance
sampling with the initial proposal function determined by a fit of a Gaussian
mixture to the MCMC samples within the variational Bayes approximation. As the
posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
components are needed; i.e., 3 components proved optimal by the variational
approximation to the model evidence.

In the most challenging run with 62 parameters, we obtain a relative effective
sample size of only 0.038\%. We want to have enough independent samples $N$ such
that the 68\% region is determined with a relative precision of about 1\%. As a
rule of thumb, we consider the ``relative error of the error'' given by
$1/\sqrt{2 N}$~\cite[ch. 37]{Agashe:2014kda}.  In the 62D case, we compute
$1.1\cdot10^6$ importance samples such that $N \approx 3500$ and the estimated
relative error of the error is 1.2\% and thus good enough for our purposes.

To create the smooth marginal plots in Figures
\ref{fig:FHvsCT}--\ref{fig:scalar:SM-EFT}, we apply kernel density estimation
for both MCMC and importance samples using the fast \texttt{figtree}
library~\cite{morariu08figtree}. In the latter case, we additionally crop 500
outliers.

The prior or posterior predictive distribution of an observable $X$ within a
model $M$ in which $X=f(\vecth)$ is a definite function of the
parameters $\vecth$ is given as
\begin{align}
  \label{eq:predictive}
  P(X | M) &= \int \rmdx{\vecth} P(X|\vecth,M) P(\vecth|M)\nn
  &= \int \rmdx{\vecth} \delta(X - f(\vecth)) P(\vecth|M) \,.
\end{align}
We estimate $P(X|M)$ by computing $f(\vecth_i)$ for every sample $\vecth_i \sim
P(\vecth|M)$, then smooth as above.
